Mreže

### 2016-04-19 presentation.tex
Dodal funkcijo za homomorfizem

\begin{column}{2cm}
  \begin{figure}
  \centering
  \begin{tikzpicture}[scale=1]
    \node (a) at (0,0) {$a$};
    \node (b) at (-1,-1) {$b$};
    \node (c) at (-1,-2) {$c$};
    \node (d) at (0,-3) {$d$};
    \node (e) at (1,-1.5) {$e$};
    \draw (a) -- (b) -- (c) -- (d) -- (e) -- (a);
  \end{tikzpicture}
  \end{figure}
\end{column}

@@

\begin{column}{5cm}
\begin{center}
$\{1,2,3,6\}, |$
\end{center}
\begin{figure}
\centering
\begin{tikzpicture}[scale=0.5]
  \node (one) at (0,2) {$6$};
  \node (a) at (-3,0) {$3$};
  \node (d) at (3,0) {$2$};
  \node (zero) at (0,-2) {$1$};
  \draw (zero) -- (a) -- (one)  -- (d) -- (zero);
\end{tikzpicture}
\end{figure}
\end{column}
\end{columns}

@@

\begin{frame}
\begin{definition}
Preslikava $f :\mathcal{L} \to \mathcal{L}'$ je \textbf{homomorfizem}, ča za poljubna $x,y \in \mathcal{L}$ velja:
\begin{itemize}
\item $f(x \lor y) = f(x) \lor f(y)$
\item $f(x \land y) = f(x) \land f(y)$
\end{itemize}
\end{definition}

@@

\begin{block}{funkcija za prej}
Funkcija za prej 
\end{block}

>>>>

\begin{column}{2cm}
  \begin{figure}
  \centering
  \begin{tikzpicture}[scale=1]
    \node (a) at (0,0) {$a$};
    \node (b) at (-1,-1) {$b$};
    \node (c) at (-1,-2) {$c$};
    \node (d) at (0,-3) {$d$};
    \node (e) at (1,-1) {$e$};
    \node (f) at (1,-2) {$f$};
    \draw (a) -- (b) -- (c) -- (d) -- (f) -- (e) -- (a);
    \draw (f) -- (b);
    \draw (c) -- (e);
  \end{tikzpicture}
  \end{figure}
\end{column}

@@

\begin{column}{5cm}
\begin{center}
$\{1,2,3,6\}, |$
\end{center}
\begin{figure}
\centering
\begin{tikzpicture}[scale=0.5]
  \node (one) at (0,2) {$6$};
  \node (a) at (-3,0) {$2$};
  \node (d) at (3,0) {$3$};
  \node (zero) at (0,-2) {$1$};
  \draw (zero) -- (a) -- (one)  -- (d) -- (zero);
\end{tikzpicture}
\end{figure}
\end{column}
\end{columns}

@@

\begin{frame}
\begin{definition}
Preslikava $f :\mathcal{L} \to \mathcal{L}'$ je \textbf{homomorfizem}, če za poljubna $x,y \in \mathcal{L}$ velja:
\begin{itemize}
\item $f(x \lor y) = f(x) \lor f(y)$
\item $f(x \land y) = f(x) \land f(y)$
\end{itemize}
\end{definition}

@@

\begin{block}{Funkcija za prej}
\begin{table}[]
\centering
\label{my-label}
\begin{tabular}{c|c}
x         & f(x) \\ \hline
$\{\}$    & $1$  \\
$\{0\}$   & $2$  \\
$\{1\}$   & $3$  \\
$\{1,2\}$ & $6$ 
\end{tabular}
\end{table}
\end{block}
